Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-04 paper/v1.0/sections/appendix_c.tex
Add contect to Appendix c

Now consider a scattering event from a $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')}$ into another $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with constant quansienergy $\varepsilon$ which has been
\begin{equation} \label{eq_c16}
  \begin{aligned}
  \psi_{\beta}(\vb{k'},t,t') &= \exp(-\frac{i}{\hbar}\varepsilon_{\beta} t)
  \phi_{\beta}(\vb{k'},t') \\
  &
  \longrightarrow
  \Psi_{\alpha}(\vb{k},t,t') = \exp(-\frac{i}{\hbar}\varepsilon t)
  \Phi_{\alpha}(\vb{k},t').
  \end{aligned}
\end{equation}
\begin{figure}[b]
  \includegraphics[scale=1.0]{figures/fig_2.pdf}
  \caption{Scattering from $\ket{\psi_{\beta}(t,t')}$ to constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to scattering potential created by impurities.}
  \label{fig_2}
\end{figure}

>>>>

Now consider a scattering event from a $t$-$t'$-Floquet state $\ket{\psi_{\beta}(t,t')} $ into another $t$-$t'$-Floquet state $\ket{\Psi_{\alpha}(t,t')}$ with constant quansienergy $\varepsilon$:
\begin{equation} \label{eq_c15}
  \begin{aligned}
  \ket{\psi_{\beta}(t,t')} &= \exp(-\frac{i}{\hbar}\varepsilon_{\beta} t)
  \ket{\phi_{\beta}(t')} \\
  &
  \longrightarrow
  \ket{\Psi_{\alpha}(t,t')} = \exp(-\frac{i}{\hbar}\varepsilon t)
  \ket{\Phi_{\alpha}(t')}.
  \end{aligned}
\end{equation}
\begin{figure}[b]
  \includegraphics[scale=1.0]{figures/fig_2.pdf}
  \caption{Scattering from $\ket{\psi_{\beta}(t,t')}$ to constant energy state $\ket{\Psi_{\alpha}(t,t')}$ due to scattering potential created by impurities.}
  \label{fig_2}
\end{figure}
It is important to remember that a state of this considering system can be represented by two independent quantum numbers: $n$ represents the landau level and $m$ represents the qunatized momentum in $x$-direction. The scattering amplitutde for this scattering scenario can be calculated using the equation derived in Eq.~(\ref{eq_c14})
\begin{equation} \label{eq_c16}
  \begin{aligned}
    a_{\alpha\beta}(t,t') =
    -\frac{i}{\hbar}
    \int_{0}^t dt_1 \;
    e^{\frac{i}{\hbar}\qty(\varepsilon_{\beta} - \varepsilon)t_1}
    \bra{\phi_{\beta}(t')}
    V(\vb{r}) \ket{\phi_{\alpha}(t')},
  \end{aligned}
\end{equation}
and assuiming for a long time $t \rightarrow \infty$, we can turn this integral into a delta distrubution
\begin{equation} \label{eq_c17}
  \begin{aligned}
    a_{\alpha\beta}(t,t') =
    -2\pi i \delta(\varepsilon_{\beta} - \varepsilon)Q,
  \end{aligned}
\end{equation}
where $Q \equiv \bra{\phi_{\beta}(t')}
V(\vb{r}) \ket{\phi_{\alpha}(t')}$ and using completeness properties we can re-write this as
\begin{equation} \label{eq_c18}
    Q =
    \sum_{\vb{k}}\sum_{\vb{k'}}
    \braket{\phi_{\beta}(t')}{\vb{k'}}
    \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}
    \braket{\vb{k}}{\phi_{\alpha}(t')},
\end{equation}
and seperating $x$ and $y$ directional momentums we can derive (we already assumed that $L_y \rightarrow \infty$)
\begin{equation} \label{eq_c19}
    Q =
    \sum_{k_x}\sum_{{k'}_x}
    \int_{-\infty}^{\infty} \int_{-\infty}^{\infty} dk_y d{k'}_y \;
    V_{\vb{k'},\vb{k}}
    \phi_{\beta}^{\dagger}(\vb{k'},t')
    \phi_{\alpha}(\vb{k},t').
\end{equation}
with $V_{\vb{k'},\vb{k}} \equiv \mel{\vb{k'}}{V(\vb{r})}{\vb{k}}$.

Since the perturbation potential $V(\vb{r})$ is assumed to be formed by an ensemble of randomly distributed impurities, consider $N_{imp}$ identical impurities positioned at randomly distributed but fixed positions $\vb{r}_i$. Then scattering potential $V(\vb{r})$ is given by the sum over uncorrelated single impurity potentials $\upsilon(\vb{r})$
\begin{equation} \label{eq_c20}
  V(\vb{r}) \equiv
  \sum_{i=1}^{N_{imp}}
  \upsilon (\vb{r}-\vb{r}_i).
\end{equation}
Next we model the perturbation $V(\vb{r})$ as a Gaussian random potential where one can choose the zero of enerrgy such that the potential is zero on average. This model is characterized by \cite{akkermans10}
\begin{subequations}
\begin{equation} \label{eq_c21a}
  \expval{\upsilon(\vb{r})}_{imp} =0
\end{equation}
\begin{equation} \label{eq_c21b}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon(\vb{r}-\vb{r'})
\end{equation}
\end{subequations}
where $\expval{\cdot}_{imp}$ denoted the average over realizations of the impurity disorder. In addition, this model assume that $\upsilon (\vb{r}-\vb{r'})$ only dependes on the position difference $|\vb{r}-\vb{r'}|$ and it decays with a characteristic leangth $r_c$. Since this study considers the case where the waveleagth of radiation or scattering electrons is much faster than $r_c$, it is a good approximation to make two-point correlation function to be
\begin{equation} \label{eq_c22}
  \expval{\upsilon(\vb{r})\upsilon(\vb{r'})}_{imp} = \Upsilon_{imp}^2\delta(\vb{r}-\vb{r'})
\end{equation}
and a random potential $V(\vb{r})$ with this property is called white noise \cite{akkermans10}. Then we can model approximately the total scattering potential as
\begin{equation} \label{eq_c23}
  V(\vb{r}) =
  \sum_{i=1}^{N_{imp}}
  \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i).
\end{equation}
Then we can calculate $V_{\vb{k'},\vb{k}}$ using this assumption as follows
\begin{subequations}
\begin{align}
 V_{\vb{k'},\vb{k}} & =
 \mel**{\vb{k'}}{\sum_{i=1}^{N_{imp}}
 \Upsilon_{imp} \delta(\vb{r}-\vb{r}_i)}{\vb{k}} \label{eq_c24a} \\
 & =
 \sum_{i=1}^{N_{imp}}
 \int_{-\infty}^{\infty} dy\; \bigg[
 \frac{1}{\sqrt{L_xL_y}} e^{ik'_y y} \delta(y-y_i) \nonumber \\
 & \times \frac{1}{\sqrt{L_xL_y}} e^{-i{k}_y y}
 \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \bigg] \label{eq_c24b} \\
  & =
 \sum_{i=1}^{N_{imp}} \frac{1}{{L_xL_y}}
 e^{i(k'_y - k_y )y}
 \mel**{k'_x}{\Upsilon_{imp} \delta(x-x_i)}{k_x} \label{eq_c24c}
\end{align}
\label{eqn:all-lines}
\end{subequations}
